\documentclass{article}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{hyperref}

\title{Curriculum Vitae}
\author{David Lawton}
\date{13th Jan. 2024}

\begin{document}

\maketitle
\vfill
\newpage
\section{Personal Details:}
Address: 39 Landscape Park, Churchtown, Dublin 14. D14 A304.\\
Contact Number: +353 83 834 4417\\
Contact Email: davidj.lawton@gmail.com\\

\section{Education:}
\begin{itemize}
\item 2008 - 2016: Scoil Barra Naofa, Beaumont.
\item 2016 - 2022: St Francis College, Rochestown. LC 2022, 625 points.
\item 2022 - Present: Trinity College Dublin, BA Theoretical Physics. Summer 2023 Grade - 1.
\end{itemize}
\section{Work Experience:}
\begin{itemize}
\item June 2022 – August 2022: Maryborough Hotel and Spa, kitchen porter. 
\item August 2023 – Present: Fota Island Resort, food and beverage assistant.
\end{itemize}
\section{Awards/Acknowledgements:}
\begin{itemize}
\item Fundraised for HOPE during secondary school.
\item Completed YMP at KOEC.
\item Achieved Bronze Gaisce Award.
\item Earned maximum points in LC 2022, including H1's in Maths, Physics, Applied Maths, Chemistry and Biology.
\item Received Exhibition Scholarship from TCD.
\end{itemize}
\section{Skills}
\begin{itemize}
\item Word/Excel proficiency.
\item Basic Python skills.
\item Basic Latex skills.
\end{itemize}
\section{Referees:}
\begin{itemize}
\item Prof. Chaolun Wu - Teaching Fellow at TCD School of Maths.
\end{itemize}
\end{document}