\documentclass{article}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{hyperref}

\hypersetup{
  colorlinks   = true,    % Colours links instead of ugly boxes
  urlcolor     = blue,    % Colour for external hyperlinks
  linkcolor    = blue,    % Colour of internal links
  citecolor    = red      % Colour of citations
}

\title{Curriculum Vitae.}
\author{David James Lawton}
\date{17th Jun. 2024}

\begin{document}

\maketitle

\section{Personal Details:}
Address 1: 39 Landscape Park, Churchtown, Dublin 14. D14 A304. (During college term)\\
Address 2: 15 Temple Vale, Ballintemple, Cork. T12 P9A2. (During holidays)
Contact Number: +353 83 834 4417\\
Contact Email: lawtond@tcd.ie\\

\section{Education:}
\begin{itemize}
\item 2008 - 2016: Scoil Barra Naofa, Beaumont.
\item 2016 - 2022: St Francis College, Rochestown. LC 2022, 625 points.
\item 2022 - Present: Trinity College Dublin, BA Theoretical Physics. 
\begin{itemize}
\item 2022/23 Grade - 1.
\item 2023/24 Grade - Fail - Re-assess at Supplemental Exams. (One repeat, II-1 expected)
\end{itemize}
\end{itemize}
\section{Work Experience:}
\begin{itemize}
\item June $\rightarrow$ August (2022): Maryborough Hotel and Spa, kitchen porter. 
\item August $\rightarrow$  September (2023), May 2024 $\rightarrow$ Present : Fota Island Resort, food and beverage assistant.
\end{itemize}
My experience in the hospitality industry really improved my ability to work as part of a collaborative effort, as well as the ability to take initiative myself, and communicate with consumers.
\section{Awards/Acknowledgements:}
\begin{itemize}
\item Fundraised for HOPE during Second-Level Education (2019).
\item Completed Young Mariners Program at KOEC (2020).
\item Achieved Bronze Gaisce Award (2020).
\item Earned maximum points in LC 2022, including H1's in Maths, Physics, Applied Maths, Chemistry and Biology.
\item Received Entrance Exhibition Award from TCD (2023).
\end{itemize}
\section{Skills}
\begin{itemize}
\item Word/Excel proficiency.
\item Maths/physics, graphing and computation skills in Python.
\item Some Mathematica experience.
\item Latex proficiency.
\item OriginLab proficiency.
\item Recently, learning Quantum Mechanics and Group Theory in my free time.
\end{itemize}
I have gained most of these skills over the past two years of my course. Some of the basic Python code I have written can be seen at \url{https://github.com/DavidLawton04/VSCode}. Of course, I would jump at the chance to improve my current skills, or add new ones.
\section{Referees:}
\begin{itemize}
\item Prof. Chaolun Wu - Teaching Fellow at TCD School of Maths. (WUCH@tcd.ie)
\end{itemize}
\end{document}